Fast approximate Bayesian inference of HIV indicators using the Naomi small-area estimation model

### 2023-06-18 src/docs_paper/paper.Rmd
Short paragraph on parallel and GPUs

>>>>

Integration of a moderate number of hyperparameters posed a particular challenge, and led to the use of quadrature grids with large number of nodes.
However, computation at each node is independent, such that the run-time of the algorithm could potentially be significantly improved by parallel computing.
Further computational speed-ups might be obtained using graphics processing units (GPUs) speciallised for the relevant matrix operations.
